Dependent Object Types

### 2012-07-04 doc/semester/report.tex
minor
fix

Syntactically, we add a widening term: $\wid t T$, and extend values
with a case for widening: $\wid v T$. The typing rule for widening,
\textsc{wid}, is the only one admitting a subtyping relaxation:
$\Gamma \ts (\wid t T) \typ T$ if $\Gamma \ts t : T'$ and $\Gamma \ts T'
\sub T$.

@@

Now, consider the term:
\begin{align*}
&\mlnew v {Tc \ldefs{m(x)=\wid x \Top}}{
(\wid v T).m(\wid v {(\wid v {A \refine z {\Ldecl B \Top \Top}})})
}
\end{align*}

When we evaluate the method invocation, we need to cast $\wid v {(\wid
  v {A \refine z {\Ldecl B \Top \Top}})}$ to $v.A$, and for this, we
need the newly introduced $\textsc{path-$\sub$}$ rule.

>>>>

Syntactically, we add a widening term: $\wid t T$, and extend values
with a case for widening: $\wid v T$. The typing rule for widening,
\textsc{wid}, is the only one admitting a subtyping relaxation:
$\Gamma \ts (\wid t T) \typ T$ if $\Gamma \ts t \typ T'$ and $\Gamma \ts T'
\sub T$.

@@

Now, consider the term:
\begin{align*}
&\mlnew v {T_c \ldefs{m(x)=\wid x \Top}}{
(\wid v T).m(\wid v {((\wid v T).{A \refine z {\Ldecl B \Top \Top}})})
}
\end{align*}

When we evaluate the method invocation, we need to cast $\wid v
{((\wid v T).{A \refine z {\Ldecl B \Top \Top}})}$ to $v.A$, and for
this, we need the newly introduced $\textsc{path-$\sub$}$ rule.
